What's in a name? On the (automated) topic naming of software maintenance activities

### 2010-03-02 icpc/icpc2010.tex
introduction

Topics in this paper and the previous paper are word bags or word distributions. These word distributions are found via Latent Dirichlet Allocation~\cite{Blei2003}, which find independent word distributions shared among documents (changelog comments). The unfortunate aspect of topics that are word distributions is that they lack the tangibility of a rose. They do not self idea themselves due to their tangible properties. Topics have to be identified by interpretting the prevelant words in the word distribution and by inspecting related documents. This is tiresome when one has to handle more than one hundred different topics. It would be nice if we could glance at a topic and have some idea what it was about. This is the power of labelling and naming.

If a topic has a name or a label we immediately understand and register what it is. In our case the name is the bit of information that was missing from our topics to make them useful and complete.

In this paper we attempt to name or label development topics that were extracted from the history of a development project. In part

In this paper we `name' and label topic models generated by a topic modeling technique, Latent Dirichlet Allocation~\cite{Blei2003}. We use these topic models to train supervised learners to classify larger datasets. We also show that these topics can be generalized across products.

% Clean this up
Traditionally topic modeling has required manual annotation to derive domain-relevant information. This paper introduces \emph{named topic models}, topic models which are named using a cross-project taxonomy. We start with an unsupervised topic learning algorithm, then manually annotate the topics using the ontology. From the annotated topics, we apply automated classifiers to find labels for the remaining topics.

Typically what is distinct is the software's particular functionality -- whether it offers email composition, prepares tax returns, and so on. What is common, however, is the non-functional, or quality requirements, that the software focuses on. Our approach makes use of software quality taxonomies in order to compare different projects on similar concepts. For example, how is the Security quality treated over time by product A versus product B? Does product A care about it more as it matures? Does the quality occur more often in software commits?

Our contributions include:
\begin{itemize}
\item  We introduce named topic analysis, and demonstrate its usefulness
  compared to other approaches.
% unsure about this
\item We show that these topics can be learned and used to classify other datasets.
\item We present a number of visualizations of named topics and their trends over time to aid
  communication and analysis.
\item We use an exploratory case study of
  several open source database systems to show how named topics can be compared between projects.
\end{itemize}

>>>>

Topics in this paper and the previous paper are word bags or word distributions. These word distributions are found via Latent Dirichlet Allocation~\cite{Blei2003}, which find independent word distributions shared among documents (changelog comments). The unfortunate aspect of topics that are word distributions is that they lack the tangibility of a rose. They do not self idea themselves due to their tangible properties. Topics have to be identified by interpretting the prevelant words in the word distribution and by inspecting related documents. This is tiresome when one has to handle more than one hundred different topics. It would be nice if we could, at a glance at , have some idea what the topic is about. This is the power of labelling and naming.

If a topic has a name or a label we immediately understand and register what it is. In our case the name is the bit of information, the summary, that was missing from our topics to make them useful and complete. Although we are convinced that accurate naming is not completely feasible, so we have focussed on labelling topics by non-functional requirements.

%In this paper we \textit{name} and \textit{label} topics generated by %a topic modeling technique, Latent Dirichlet %Allocation~\cite{Blei2003}. We use these topic models to train %supervised learners to classify larger datasets. We also show that %these topics can be generalized across products.

% Clean this up
Traditionally topic extraction has required manual annotation to derive domain-relevant information. This paper attempts to implement \emph{labelled topic extraction}, topic extracted are given labels relating to a cross-project taxonomy. This is an ontological approach where we attempt to relate networks of words to labels and then search for these terms in our topic. We also compare this approach to machine leaners.
%We start with an unsupervised topic learning algorithm, then manually %annotate the topics using the ontology. From the annotated topics, we %apply automated classifiers to find labels for the remaining topics.

% XXX Not sure about this
\begin{comment}
Typically what is distinct is the software's particular functionality -- whether it offers email composition, prepares tax returns, and so on. What is common, however, is the non-functional, or quality requirements, that the software focuses on. Our approach makes use of software quality taxonomies in order to compare different projects on similar concepts. For example, how is the Security quality treated over time by product A versus product B? Does product A care about it more as it matures? Does the quality occur more often in software commits?
\end{comment}

Our contributions include:
\begin{itemize}
\item  We introduce labelled topic extraction, and demonstrate its usefulness
  compared to other approaches.
% unsure about this
\item We show that these topics can be learned and used to classify other datasets.
\item We present a number of visualizations of named topics and their trends over time to aid
  communication and analysis.
\item We use an exploratory case study of
  several open source database systems to show how named topics can be compared between projects.
\end{itemize}
